Draft Exploration

### 2020-05-06 draft_exploration.Rmd
added college condition and explanation to career peak

peak_level <- function(max_round, startyear, endyear, min_round = 1) {

top_20_hs <- master %>%
  filter(source == "H" & draft_numb == 1) %>%
  filter(draft_round >= min_round & draft_round <= max_round & year >= startyear & year <= endyear) %>%
  mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
                             "<=College",
                             high_level)) %>%
  group_by(signed, high_level) %>%
  summarize(n = n()) %>%
  group_by(signed) %>%
  mutate(y = n/sum(n)) %>%
  mutate(high_level = factor(high_level,levels = c("<=College",
                                                   "Indy",
                                                   "Rk",
                                                   "A-",
                                                   "A",
                                                   "A+",
                                                   "AA",
                                                   "AAA",
                                                   "MLB")))

@@

peak_level(max_round = 20, startyear = 2010, endyear = 2010, min_round = 1)
```

@@

>>>>

peak_level <- function(max_round, startyear, endyear, min_round = 1, beyond_college = "") {

top_20_hs <- master %>%
  filter(source == "H" & draft_numb == 1) %>%
  filter(draft_round >= min_round & draft_round <= max_round & year >= startyear & year <= endyear) %>%
  mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
                             "<=College",
                             high_level)) %>%
  filter(high_level != beyond_college) %>%
  group_by(signed, high_level) %>%
  summarize(n = n()) %>%
  group_by(signed) %>%
  mutate(y = n/sum(n)) %>%
  mutate(high_level = factor(high_level,levels = c("<=College",
                                                   "Indy",
                                                   "Rk",
                                                   "A-",
                                                   "A",
                                                   "A+",
                                                   "AA",
                                                   "AAA",
                                                   "MLB")))

@@

peak_level(max_round = 20, startyear = 1990, endyear = 2010, min_round = 1, beyond_college = "")
```

@@

```{r}
master %>%
  filter(source == "H" & draft_numb == 1) %>%
  mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
                             "<=College",
                             high_level)) %>%
  filter(signed == "Y" & high_level == "<=College" & year <= 2018) %>%
  arrange(desc(year))
```

```{r}
master %>%
  filter(year %in% c(1990:2010) & draft_round %in% c(1:20)) %>%
  filter(source == "H" & draft_numb == 1) %>%
  mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
                             "<=College",
                             high_level)) %>%
  filter(signed == "N" & high_level != "<=College" & high_level != "Indy") %>%
  summarize(percent_MLB = sum(high_level == "MLB") / n())
```
